Graph Convolution Networks

### 2017-09-01 Work_report/Presentation/GCN/gcn_presentation.tex
Some updates to the gcn presentation

\documentclass{beamer}
\usetheme{Boadilla}
% \usepackage[a4paper, tmargin=1in, bmargin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{parskip}
\usepackage{pdflscape}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{float}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{amssymb}

\mode<presentation>{
    \AtBeginSection[]
    {
    \begin{frame}[allowframebreaks]{Outline}
    \tableofcontents[currentsection]
    \end{frame}
    }
}
% \AtBeginSubsection[
%   {\frame<beamer>{\frametitle{Outline}
%     \tableofcontents[currentsection,currentsubsection]}}%
% ]%
% {
%   \frame<beamer>{
%     \frametitle{Outline}
%     \tableofcontents[currentsection,currentsubsection]}
% }

@@

% \subsection{Results on MNIST}
\begin{frame}
  \frametitle{MNIST results}
  \begin{itemize}
  \item Achieves close to classical CNN accuracy.
  \item Pictures to be added.
  \end{itemize}
\end{frame}

\section{Semi-Supervised Classification with Graph Convolutional Networks}
\begin{frame}
  \frametitle{Fast approximate convolutions on the graph}
  \begin{itemize}
  \item Layerwise propagation rule as
    $$H^{(l+1)} = \sigma(\tilde{D}^{-1/2}\tilde{A}\tilde{D}^{-1/2}H^{(l)}W^{(l)})$$
    Here $\tilde{A} = A + I_N$ the adjacency matrix with added self-loops. $\tilde{D}$ is the degree matrix.
  \item In the chebyshev approximation, limit to $K=1$ and therefore the layer-wise convolution operation is linear function of the laplacian.
  \item Experimentally shows 2-3 layered GCN can effectively learn standard graph problems. Specifically it does decently well in the unsupervised case, and significantly good in the semi-supervised setting.
  \end{itemize}
\end{frame}

>>>>

\documentclass{beamer}
\usetheme{Boadilla}
% \usepackage[a4paper, tmargin=1in, bmargin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{parskip}
\usepackage{pdflscape}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{float}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{amssymb}
\usepackage{multirow}
\mode<presentation>{
    \AtBeginSection[]
    {
    \begin{frame}[allowframebreaks]{Outline}
    \tableofcontents[currentsection]
    \end{frame}
    }
}
% \AtBeginSubsection[
%   {\frame<beamer>{\frametitle{Outline}
%     \tableofcontents[currentsection,currentsubsection]}}%
% ]%
% {
%   \frame<beamer>{
%     \frametitle{Outline}
%     \tableofcontents[currentsection,currentsubsection]}
% }

@@

% \subsection{Results on MNIST}
\begin{frame}
  \frametitle{MNIST results}
  \begin{itemize}
  \item Achieves close to classical CNN accuracy.
    % \item Pictures to be added.
    \begin{table}[H]
      \centering
      \caption{MNIST performance}
      \label{t:mn_perf}
      \begin{tabular}{|l|l|l|l|l|l|l|l|}
        \hline
        \multicolumn{2}{|l|}{accuracy} & \multicolumn{2}{l|}{loss} & \multirow{2}{*}{name}       \\ \cline{1-4}
        test           & train         & test        & train       &                             \\ \hline
        98.87          & 99.62         & 1.02e+00    & 9.99e-01    & cgconv\_cgconv\_fc\_softmax \\ \hline
        98.00          & 99.26         & 6.52e-02    & 2.77e-02    & cgconv\_softmax             \\ \hline
        96.75          & 96.78         & 1.12e+00    & 1.12e+00    & fgconv\_fgconv\_fc\_softmax \\ \hline
        95.91          & 95.50         & 1.44e-01    & 1.53e-01    & fgconv\_softmax             \\ \hline
        97.66          & 97.79         & 1.09e+00    & 1.08e+00    & sgconv\_sgconv\_fc\_softmax \\ \hline
        96.95          & 97.27         & 1.03e-01    & 9.46e-02    & sgconv\_softmax             \\ \hline
        92.18          & 92.47         & 3.14e-01    & 3.14e-01    & softmax                     \\ \hline
      \end{tabular}
    \end{table}
\end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Accuracy and Loss Plots}
  \begin{figure}[H]
    \centering
    \includegraphics[scale=0.38]{images/accuracy_plot.png}
    \caption{Accuracy and Loss function plot}
    \label{fig:acl_mnist}
  \end{figure}

\end{frame}
\section{Semi-Supervised Classification with Graph Convolutional Networks}
\begin{frame}
  \frametitle{Fast approximate convolutions on the graph}
  \begin{itemize}
  \item Layerwise propagation rule as
    $$H^{(l+1)} = \sigma(\tilde{D}^{-1/2}\tilde{A}\tilde{D}^{-1/2}H^{(l)}W^{(l)})$$
    Here $\tilde{A} = A + I_N$ the adjacency matrix with added self-loops. $\tilde{D}$ is the degree matrix.
  \item In the chebyshev approximation, limit to $K=1$ and therefore the layer-wise convolution operation is linear function of the laplacian.
  \item Experimentally shows 2-3 layered GCN can effectively learn standard graph problems. Specifically it does decently well in the unsupervised case, and significantly good in the semi-supervised setting.
  \end{itemize}
\end{frame}
